Variational Monte Carlo on bosonic systems

### 2018-01-25 project_1/article/article.tex
Move nabla-operator outside bra-ket
Break line with gradient of Slater permanent
Add general expression for the Laplacian

                \bra{\vf{r}}\nabla_i\ket{\Psi_T}

@@

                \bra{\vf{r}}\nabla_i^2\ket{\Psi_T}

@@

                \frac{2\bra{\vf{r}}\nabla_i\ket{\Psi_T}}

@@

            where $\ket{\Phi_T}$ is the same Slater permament as in

@@

                \bra{\vf{r}}\nabla_k\ket{\Psi_T}

@@

            The gradient of the Slater permament gives

@@

                \prod_{i \neq k}^N\phi(\vf{r}_i)
                = \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}

@@

@@

                    \nabla_k u(r_{mk}) \nonumber \\

@@

%            \begin{align}
%                &=
%                \Biggl\{
%                    \nabla_k
%                    \prod_i^N\phi(\vf{r}_i)
%                \Biggr\}
%                \exp\Biggl(
%                    \sum_{j < l}^N u(r_{jl})
%                \Biggr)
%                +
%                \bra{\vf{r}}\ket{\Phi_T}
%                \nabla_k
%                \exp\Biggl(
%                    \sum_{j < l}^N u(r_{jl})
%                \Biggr) \\
%                &=
%                \Biggl\{
%                    \nabla_k\phi(\vf{r}_k)
%                    \prod_{i \neq k}^N \phi(\vf{r}_i)
%                \Biggr\}
%                \exp\Biggl(
%                    \sum_{j < l}^N u(r_{jl})
%                \Biggr)
%                +
%                \bra{\vf{r}}\ket{\Psi_T}
%                \nabla_k
%                \Biggl(
%                    \sum_{m < n}^N u(r_{mn})
%                \Biggr).
%            \end{align}
%            The last term is extracted from the chain rule and can be
%            evaluated as
%            \begin{align}
%                \nabla_k
%                    \sum_{m < n}^N u(r_{mn})
%                &=
%                \sum_{m = 1}^{k - 1}
%                \nabla_k u(r_{mk})
%                +
%                \sum_{n = k + 1}^N
%                \nabla_k u(r_{kn}) \\
%                &=
%                \sum_{m \neq k}^N\nabla_k u(r_{km}),
%            \end{align}

@@

                \bra{\vf{r}}\ket{\Psi_T} \nonumber \\

@@

@@

%            \begin{align}
%                \bra{\vf{r}}\nabla_k\ket{\Psi_T}
%                &=
%                \Biggl\{
%                    \nabla_k\phi(\vf{r}_k)
%                    \prod_{i \neq k}^N \phi(\vf{r}_i)
%                \Biggr\}
%                \exp\Biggl(
%                    \sum_{j < k}^N u(r_{jk})
%                \Biggr)
%                +
%                \bra{\vf{r}}\ket{\Psi_T}
%                \sum_{m \neq k}^N\nabla_k u(r_{km}).
%            \end{align}

>>>>

                \nabla_i\bra{\vf{r}}\ket{\Psi_T}

@@

                \nabla_i^2\bra{\vf{r}}\ket{\Psi_T}

@@

                \frac{2\nabla_i\bra{\vf{r}}\ket{\Psi_T}}

@@

            where $\ket{\Phi_T}$ is the same Slater permanent as in

@@

@@

            The gradient of the Slater permanent gives

@@

                \prod_{i \neq k}^N\phi(\vf{r}_i) \\
                &= \frac{\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}

@@

            \begin{widetext}

@@

                        \nabla_k u(r_{mk})

@@

@@

                    \sum_{m \neq k}^N\nabla_k u(r_{km}) \\
                    \Biggr)
                We can now find the Laplacian of the trial wavefunction. This
                gives
                    \nabla_k^2\bra{\vf{r}}\ket{\Psi_T}
                    &= \nabla_k\nabla_k\bra{\vf{r}}\ket{\Psi_T}
                    = \nabla_k
                    \Biggr)
                    \bra{\vf{r}}\ket{\Psi_T} \\
                        \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
                        + \left[
                            \nabla\frac{1}{\phi(\vf{r}_k)}
                        \right]
                        \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
                    \Biggr)

@@

                    \Biggr)
                    \nabla_k\bra{\vf{r}}\ket{\Psi_T} \\
                        \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
                        - \left[
                        \right]^2
                        \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
                    \Biggr)
                    \Biggr)^2

@@

                We now divide by the trial wavefunction. This simplifies the
                calculations and is more similar to the expression for the local
                energy.
                    \frac{\nabla_k^2\bra{\vf{r}}\ket{\Psi_T}}
                    {\bra{\vf{r}}\ket{\Psi_T}}
                    \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
                    - \left[
                    \right]^2
                    \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
                    \Biggr)^2 \\
                    \frac{\nabla_k^2\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
                    \sum_{m \neq k}^N\nabla_k^2 u(r_{km})
                    \frac{2\nabla_k\phi(\vf{r}_k)}{\phi(\vf{r}_k)}
                    \Biggr)^2
            \end{widetext}
